### 2022-10-31 inst/Examples/Paper_results/Paper_results_2.Rmd
Changes to markdown files for reproducing results
and for using some october github action minutes

The data used is the NGRIP/GICC05 data set 'NGRIP_d18O_and_dust_5cm', downloaded from [Centre for Ice and Climate](iceandclimate.nbi.ku.dk) at the Niels Bohr Institute of the University of Copenhagen, Denmark, and the table of stadial-interstadial events presented by [Rasmussen et al. (2014)](https://www.sciencedirect.com/science/article/pii/S0277379114003485). These are included in the package and can be imported as follows. 
```{r initialize, eval=FALSE}
#library(bremla)
data("event_intervals")
data("events_rasmussen")
data("NGRIP_5cm")
age = NGRIP_5cm$age
depth = NGRIP_5cm$depth
proxy = NGRIP_5cm$d18O
n=length(diff(age))
data = data.frame(age=age,dy=c(NA,diff(age)),depth=depth,depth2=depth^2,proxy=proxy)
events=list(locations = events_rasmussen$depth,
            locations_unit="depth",degree=1)
plot(depth,proxy,xlab="Age (yb2k)",ylab=expression(paste(d^18,"O (permil)")),type="l",
     xlim=rev(range(depth)))+abline(v=events$locations,col="gray",lwd=0.7)
formula = dy~-1+depth2+proxy
```

@@

```{r adolphi, eval=TRUE}
adolphipdfs = adolphiloader(tieshifts=c(11050,12050,13050,22050,42050),plotdens = TRUE,
                            x.ref=c(11050,12050,13050,22050,42050))
```

@@

  plot(results$fitting$inla$hyperparameters$posteriors$phi,type="l",xlab=expression(phi),ylab="Density")
  abline(v=results$fitting$inla$hyperparameters$results$phi$mean)
  abline(v=c(results$fitting$inla$hyperparameters$results$phi$quant0.025,
             results$fitting$inla$hyperparameters$results$phi$quant0.975),
             col="red")
 par(mfrow=c(1,1)) 
}
```

@@

```{r sync, eval = TRUE}
library(ggplot2)
synchronization = list(method="adolphi",nsims=nsims,
                       locations=c(#1492.50,
                                   1502.80,1532.70,1767.25,2132.40),
                       locations_unit="depth")
results_sync = bremla(formula,data,reference.label="GICC05",
                nsims=nsims,
                events=events,
                synchronization=synchronization,
                control.fit=list(noise="ar1"),
                control.sim=list(synchronized=TRUE,summary=list(CI.type="hpd")) ,
                print.progress=TRUE
                )
tiepointranges = as.data.frame(matrix(NA,nrow=5,ncol=3))
gicc05=results_sync$original.chron$age[1+1:n]
gicc05tie = gicc05[results_sync$tie_points$locations_indexes]
colnames(tiepointranges)=c("lower","upper","depth")
for(i in 2:5){
  tiepointranges[i,1:2] = inla.hpdmarginal(0.95,adolphipdfs[[paste0("tie",i)]])-gicc05tie[i]
}
tiepointranges[,3] = depth[results_sync$tie_points$locations_indexes]
{

@@

```{r events_individual, eval=FALSE}
eventnumber=13 #number between 1 and 29. specifies which transition to consider
#load data window and specifics to transition
lowerints = which.index(event_intervals$depth_int_lower.m, depth[2:length(depth)])
upperints = which.index(event_intervals$depth_int_upper.m, depth[2:length(depth)])
depth.reference = event_intervals$NGRIP_depth_m[eventnumber]
age.reference = event_intervals$GICC_age.yb2k[eventnumber]
interval = lowerints[eventnumber]:upperints[eventnumber]
transitionlabel = str_sub(event_intervals$onsetlabel[eventnumber],
                      str_locate(event_intervals$onsetlabel[eventnumber],"GI")[1])
control.linramp=list(proxy=proxy,
                     interval=interval,
                     interval.unit="index",
                     depth.reference=event_intervals$NGRIP_depth_m[eventnumber]
                     )
results_event = linrampfitter(results_sync,control.linramp)
control.transition_dating = list(label="Simulated transition")
results_event = events_depth_to_age(results_event,
                                    control.transition_dating=control.transition_dating)
{
  layout(mat=matrix(c(1,2,1,3),nrow=2))
  par(mar=c(5,4,4,2)+0.1)

  plot(depth[interval],proxy[interval],type="l",col="gray",
     main=paste0("(a) ",transitionlabel," linear ramp fit"),
     xlab="Depth (m)", ylab=expression(paste(delta^18,"O (permil)")),
     xlim = rev(range(depth[interval]))
     )
lines(results_event$linramp$data$x,results_event$linramp$linrampfit$mean,lwd=1.5)
lines(results_event$linramp$data$x,results_event$linramp$linrampfit$q0.025,lwd=1.5,col="red")
lines(results_event$linramp$data$x,results_event$linramp$linrampfit$q0.975,lwd=1.5,col="red")
abline(v=depth.reference,lty=3,lwd=0.7,col="black")
ybottom = min(results_event$linramp$data$y)
ytop = min(results_event$linramp$linrampfit$q0.025)
margt0=results_event$linramp$param$t0$marg.t0
normt0.y = margt0[,2]/diff(range(margt0[,2]))*(ytop-ybottom)-min(margt0[,2])+ybottom
lines(x=margt0[,1],y=normt0.y,col="blue",lwd=2)
ybottom = min(results_event$linramp$data$y)
ytop = min(results_event$linramp$linrampfit$q0.025)
margt1 = results_event$linramp$param$t1$marginal
normt1.y = margt1[,2]/diff(range(margt1[,2]))*(ytop-ybottom)-min(margt1[,2])+ybottom
lines(x=margt1[,1],y=normt1.y,col="blue",lwd=2,lty=3)
plot(results_event$linramp$param$t0$marg.t0,type="l",xlab=expression(paste("Onset depth (m)")),ylab="Density",
     main="(b) Marginal posterior of onset depth")#, 
     #xlim=rev(range(depth.reference,results_event$linramp$param$t0$marg.t0[,1])))
#abline(v=depth.reference,lty=3)
abline(v=results_event$linramp$param$t0$mean,lwd=1.5)
abline(v=results_event$linramp$param$t0$q0.025,col="red")
abline(v=results_event$linramp$param$t0$q0.975,col="red")
plot(results_event$linramp$param$t1$marginal,type="l",xlab=expression(paste("End point depth (m)")),ylab="Density",
     main="(c) Marginal posterior of end point depth")#, 
     #xlim=rev(range(depth.reference,results_event$linramp$param$t0$marg.t0[,1])))
#abline(v=depth.reference,lty=3)
abline(v=results_event$linramp$param$t1$mean,lwd=1.5)
abline(v=results_event$linramp$param$t1$q0.025,col="red")
abline(v=results_event$linramp$param$t1$q0.975,col="red")
par(mfrow=c(1,1),mar=c(5,4,4,2)+0.1)
hist(results_event$event_dating$samples,main=paste0(transitionlabel," Onset age"),
     xlab="Onset age (yr b2k)",col="orange",xlim=rev(range(results_event$event_dating$samples)), breaks=40, freq=0)
abline(v=age.reference,lty=3)
abline(v=results_event$event_dating$mean,lwd=2)
abline(v=results_event$event_dating$q0.025,lwd=2,col="red")
abline(v=results_event$event_dating$q0.975,lwd=2,col="red")
}
```

@@

```{r events_import, eval=FALSE}
library(readxl)
rasmussen_depths = event_intervals$NGRIP_depth_m
rasmussen_ages = event_intervals$GICC_age.yb2k #GISevents$`Age (a b2k)`
buizert_onsets = read_excel("inst/Examples/Paper_results/data/Buizert_onsets.xlsx",
                            col_types=c("text","numeric","numeric","numeric","numeric"))
buizert_depths = buizert_onsets$Depth; buizert_ages = buizert_onsets$Age
#buizert_depths[c(2:6,8:9,12:13,15:17,19:21)]
buizert_ages = buizert_ages[c(2:6,8:9,12:13,15:17,19:21)]
capron_onsets_NGRIP_d18O = read_excel("inst/Examples/Paper_results/data/Capron_onsets.xls",
                           sheet="d18O",n_max=25)
capron_ages_NGRIP_d18O = capron_onsets_NGRIP_d18O$`t1 (50%)`
capron_onsets_NGRIP_dust = read_excel("inst/Examples/Paper_results/data/Capron_onsets.xls",
                                sheet="Ca2+",n_max=24)
capron_ages_NGRIP_dust = capron_onsets_NGRIP_dust$`t1 (50%)`
capind = numeric(29); buiind = numeric(29)
capind = c(NA,2,3, 4,5,6,NA,NA,7,8,NA,9,10,11,NA,NA,NA,NA,NA,12,13,14,NA,NA,15,NA,NA,16,17)
buiind = c(NA,2,NA,3,4,6,NA,NA,8,9,NA,11,12,13,NA,NA,NA,NA,NA,15,16,17,NA,NA,19,NA,NA,20,21)
```

We then estimate the dating uncertainty for all 29 events
```{r compare_transitions_1}
agesimmatrix_d18O = matrix(NA,29,nsims)
depthlist_d18O = c()
do.plot.rampfit = TRUE
do.plot.agehist = FALSE
depthstats = as.data.frame(matrix(NA,4,29))
colnames(depthstats) = c("true", "mean", "CIL","CIU","dustmean","dustCIL","dustCIU")
agestats = as.data.frame(matrix(NA,4,29))
colnames(agestats) = c("true", "mean", "CIL","CIU","dustmean","dustCIL","dustCIU")
steplengths = rep(0.01,29)
steplengths[21]=0.001 #sometimes changing the steplength slightly might improve convergence (default is 0.01)
for(eventnumber in 1:29){
  transitionlabel = str_sub(event_intervals$onsetlabel[eventnumber],
                      str_locate(event_intervals$onsetlabel[eventnumber],"GI")[1])
  lowerints = which.index(event_intervals$depth_int_lower.m, results_sync$data$depth)
  upperints = which.index(event_intervals$depth_int_upper.m, results_sync$data$depth)
  interval = lowerints[eventnumber]:upperints[eventnumber]

@@

  control.transition_dating=list(label="d18O")
  agetemp_d18O = events_depth_to_age(temp_d18O,control.transition_dating)

  agesimmatrix_d18O[eventnumber,] = agetemp_d18O$event_dating$samples 
  if(do.plot.agehist){
    hist(agesimmatrix_d18O[eventnumber,],freq=0,breaks=50,col="orange",main=paste0("Onset age: ",transitionlabel),xlab="Age (yb2k)")
    abline(v=age.reference,col="blue")
  }

@@

```{r compare_transitions_2}
{
par(mfrow=c(5,6),mar=c(2,2,1.5,1))
for(i in 1:29){
  dens = density(agesimmatrix_d18O[i,])
  dens = data.frame(x=dens$x,y=dens$y)#/max(dens2$y))
  xlim = range(dens$x,event_intervals$GICC_age.yb2k[i]);ylim = range(dens$y)

  if(!is.na(buiind[i])) xlim=range(xlim,buizert_onsets$Age[buiind[i]])
  if(!is.na(capind[i])) xlim=range(xlim,capron_ages_NGRIP_d18O[capind[i]])
  #par(mar=c(2,2,1.5,1))

  plot(dens,type="l",col=1,xlab="Onset year (b2k)",ylab="Density",
       main=str_sub(event_intervals[i,2],str_locate(event_intervals[i,2],"GI-")[1]),
       xlim=xlim,ylim=ylim)
  #Axis(side=1,labels=FALSE,at=dens1$x,tck=0.1)

  #lines(dens,type="l",col="gray")
  if(FALSE){#95% credible intervals
    abline(v=mean(agesimmatrix_dust[i,]),col=1)
    zdens1 = inla.zmarginal(dens1,silent = TRUE)
    abline(v=c(zdens1$quant0.025,zdens1$quant0.975),col=1,lty=3,lwd=0.8)
    abline(v=mean(agesimmatrix_d18O[i,]),col=2)
    zdens2 = inla.zmarginal(dens2,silent = TRUE)
    abline(v=c(zdens2$quant0.025,zdens2$quant0.975),col=2,lty=3,lwd=0.8)
  }

  abline(v=event_intervals$GICC_age.yb2k[i],col="blue")  
  if(!is.na(buiind[i])){
    abline(v=buizert_onsets$Age[buiind[i]],col="green")
    #abline(v=buizert_ages[buiind[i]],col="green")
  }

  # abline(v=capron_ages_NGRIP_d18O,col="orange")
  # abline(v=capron_ages_NGRIP_dust,col="orange",lty=3)
  if(!is.na(capind[i])){
    abline(v=capron_ages_NGRIP_d18O[capind[i]],col="red")
  }

}
par(mar=c(0,0,0,0));plot(-1,axes=FALSE,xlab="",ylab="",xlim=c(0,1),ylim=c(0,1))
legend(0,1,legend=c("Onset posterior distribution",#"Ca2+ onset posterior",
                    "Rasmussen onset","Buizert onset",
                    "Capron onset"),#"Capron Ca2+ onset"),
       col=c("black", "blue", "green", "red"),
       lty=c(1,1,1,1,1,1), cex=1,bty="n")
par(mfrow=c(1,1),mar=c(5,4,4,2)+0.1)
}
rownames=c()
for(i in 1:29){
  rownames=c(rownames,str_sub(event_intervals[i,2],str_locate(event_intervals[i,2],"GI-")[1]))
}
#colnames = colnames(depthstats)[1:4]
#colnames = c("name","d18O_mean","d18O_q0.025","d18O_q0.975")
depthresults = t(depthstats)[,2:4]
colnames(depthresults)=c("Z* mean", "Z* q0.025","Z* q0.975")
ageresults = t(agestats[2:4,])
colnames(ageresults)=c("Y* mean", "Y* q0.025","Y* q0.975")
allresults = cbind(depthresults,ageresults)
rownames(allresults)=rownames
latexstr = "Event & Z^* mean (m) & Z^* 95\\% CI (m) & Y^* mean (yb2k) & Y^* 95\\% CI (yb2k) \\\\ \n"
for(i in 1:29){
  latexstr = paste0(latexstr,rownames[i], "& ", format(round(allresults[i,1],2),nsmall=2)," & (", format(round(allresults[i,2],2),nsmall=2), ",
         ",format(round(allresults[i,3],2),nsmall=2),") & ", format(round(allresults[i,4],2),nsmall=2)," & (",format(round(allresults[i,5],2),nsmall=2),", ",format(round(allresults[i,6],2),nsmall=2),") \\\\ \n"
         )
}
cat(latexstr)
```

@@

# Fixed tie-points
ntie = 3
tiesims = matrix(NA,nrow=nsims,ncol=ntie)
tiedepths = c(100,300,600)
tieoffset = c(-50,0,100)
#tieage = c(450,3000,8500)
tieage = y[tiedepths]+tieoffset

>>>>

The data used is the NGRIP/GICC05 data set 'NGRIP_d18O_and_dust_5cm', downloaded from [Centre for Ice and Climate](iceandclimate.nbi.ku.dk) at the Niels Bohr Institute of the University of Copenhagen, Denmark, and the table of stadial-interstadial events presented by [Rasmussen et al. (2014)](https://www.sciencedirect.com/science/article/pii/S0277379114003485). These are included in the package and can be imported as follows. 
```{r initialize, eval=FALSE}
#library(bremla)
data("event_intervals")
data("events_rasmussen")
data("NGRIP_5cm")
age = NGRIP_5cm$age
depth = NGRIP_5cm$depth
proxy = NGRIP_5cm$d18O
n=length(diff(age))
data = data.frame(age=age,dy=c(NA,diff(age)),depth=depth,depth2=depth^2,proxy=proxy)
events=list(locations = events_rasmussen$depth,
            locations_unit="depth",degree=1)
# plot(depth,proxy,xlab="Age (yb2k)",ylab=expression(paste(d^18,"O (permil)")),type="l",
     # xlim=rev(range(depth)))+abline(v=events$locations,col="gray",lwd=0.7)
formula = dy~-1+depth2+proxy
```

@@

```{r adolphi, eval=TRUE}
library(ggplot2)
x.ref=c(11050,12050,13050,22050,42050)
adolphipdfs = adolphiloader(tieshifts=c(11050,12050,13050,22050,42050),plotdens = FALSE,
                            x.ref=x.ref)
lower = c(-77.53, -30.92, -12.37, 336.19, 101.51)+x.ref
upper = c(-41.09, 11.94, 21.99, 714.03, 509.08)+x.ref
means = c(-59.95, -7.04, 3.34, 521.44, 275.24)+x.ref
medians = c(-60.10, -6.42, 2.64, 532.36, 243.57)+x.ref
gg1 = ggplot(data=adolphipdfs$tie1,aes(x=x,y=y))+geom_line()+theme_bw()+xlab("GICC05 age (yb2k)")+
  ggtitle("Tie-point 1") + ylab("Density") + 
  geom_vline(aes(xintercept=x.ref[1]),color="black")+
  geom_vline(aes(xintercept=means[1]),color="blue")+
  geom_vline(aes(xintercept=lower[1]),color="red")+
  geom_vline(aes(xintercept=upper[1]),color="red")
gg2 = ggplot(data=adolphipdfs$tie2,aes(x=x,y=y))+geom_line()+theme_bw()+xlab("GICC05 age (yb2k)")+
  ggtitle("Tie-point 2") + ylab("Density") + 
  geom_vline(aes(xintercept=x.ref[2]),color="black")+
  geom_vline(aes(xintercept=means[2]),color="blue")+
  geom_vline(aes(xintercept=lower[2]),color="red")+
  geom_vline(aes(xintercept=upper[2]),color="red")
gg3 = ggplot(data=adolphipdfs$tie3,aes(x=x,y=y))+geom_line()+theme_bw()+xlab("GICC05 age (yb2k)")+
  ggtitle("Tie-point 3") + ylab("Density") + 
  geom_vline(aes(xintercept=x.ref[3]),color="black")+
  geom_vline(aes(xintercept=means[3]),color="blue")+
  geom_vline(aes(xintercept=lower[3]),color="red")+
  geom_vline(aes(xintercept=upper[3]),color="red")
gg4 = ggplot(data=adolphipdfs$tie4,aes(x=x,y=y))+geom_line()+theme_bw()+xlab("GICC05 age (yb2k)")+
  ggtitle("Tie-point 4") + ylab("Density") + 
  geom_vline(aes(xintercept=x.ref[4]),color="black")+
  geom_vline(aes(xintercept=means[4]),color="blue")+
  geom_vline(aes(xintercept=lower[4]),color="red")+
  geom_vline(aes(xintercept=upper[4]),color="red")
gg5 = ggplot(data=adolphipdfs$tie5,aes(x=x,y=y))+geom_line()+theme_bw()+xlab("GICC05 age (yb2k)")+
  ggtitle("Tie-point 5") + ylab("Density") + 
  geom_vline(aes(xintercept=x.ref[5]),color="black")+
  geom_vline(aes(xintercept=means[5]),color="blue")+
  geom_vline(aes(xintercept=lower[5]),color="red")+
  geom_vline(aes(xintercept=upper[5]),color="red")

library(ggpubr)
ggarrange(ggarrange(gg1,gg2,gg3,nrow=1),
          ggarrange(gg4,gg5,nrow=1),
          nrow=2)
# ggsave("adolphipdfs-4800x2000.eps", device=cairo_ps,width=4800,height=2400,units="px",dpi=500,limitsize=FALSE)

@@

  plot(results$fitting$inla$hyperparameters$posteriors$phi,type="l",xlab=expression(phi),ylab="Density")
  abline(v=results$fitting$inla$hyperparameters$results$phi$mean)
  abline(v=c(results$fitting$inla$hyperparameters$results$phi$quant0.025,
             results$fitting$inla$hyperparameters$results$phi$quant0.975),
             col="red")
 par(mfrow=c(1,1)) 
}

ggp = ggplot() + theme_bw() + xlim(rev(range(results$data$age)))+
  xlab("GICC05 (yb2k)")+ylab(expression(paste(delta^18,"O (permil)")))
nevents=results$.args$events$nevents
agestarts = numeric(nevents)
for(i in 1:nevents){
  indexes = which(results$data[[paste0("psi0_",i)]]>0)
  age_i = results$data$age[indexes]
  agestarts[i]=age_i[1]
  proxy_i = results$data$proxy[indexes]
  if(i %% 2 ==0 ){
    color="red"
  }else{
    color="blue"
  }
  ggp = ggp + geom_line(data=data.frame(age_i=age_i,proxy_i=proxy_i),
                        mapping=aes(x=age_i,y=proxy_i),col=color)
}
agestarts[nevents]=last(results$data$age)
ggp = ggp + geom_vline(xintercept = agestarts,col="black",size=0.15)
print(ggp)
# ggsave("proxyplot-4800x2000.eps", device=cairo_ps,width=4800,height=2000,units="px",dpi=500,limitsize=FALSE)

@@

```{r sync, eval = TRUE}
library(ggplot2)
library(INLA)
synchronization = list(method="adolphi",nsims=nsims,
                       locations=c(#1492.50,
                                   1502.80,1532.70,1767.25,2132.40),
                       locations_unit="depth")
results_sync = bremla(formula,data,reference.label="GICC05",
                nsims=nsims,
                events=events,
                synchronization=synchronization,
                control.fit=list(noise="ar1"),
                control.sim=list(synchronized=2,summary=list(CI.type="hpd")) ,
                print.progress=TRUE
                )
tiepointranges = as.data.frame(matrix(NA,nrow=4,ncol=3))
gicc05=results_sync$original.chron$age[1+1:n]
gicc05tie = gicc05[results_sync$tie_points$locations_indexes]
colnames(tiepointranges)=c("lower","upper","depth")
for(i in 1:4){
  tiepointranges[i,1:2] = inla.hpdmarginal(0.95,adolphipdfs[[paste0("tie",i+1)]])-gicc05tie[i]
}
tiepointranges[,3] = depth[results_sync$tie_points$locations_indexes]
{

@@

```{r events_individual, eval=FALSE}
eventnumber=13 #number between 1 and 29. specifies which transition to consider
#load data window and specifics to transition
lowerints = which.index(event_intervals$depth_int_lower.m, depth[2:length(depth)])
upperints = which.index(event_intervals$depth_int_upper.m, depth[2:length(depth)])
depth.reference = event_intervals$NGRIP_depth_m[eventnumber]
age.reference = event_intervals$GICC_age.yb2k[eventnumber]
interval = lowerints[eventnumber]:upperints[eventnumber]
transitionlabel = str_sub(event_intervals$onsetlabel[eventnumber],
                      str_locate(event_intervals$onsetlabel[eventnumber],"GI")[1])
control.linramp=list(proxy=proxy,
                     interval=interval,
                     interval.unit="index",
                     depth.reference=event_intervals$NGRIP_depth_m[eventnumber]
                     )
results_event = linrampfitter(results_sync,control.linramp)
control.transition_dating = list(label="Simulated transition")
results_event = events_depth_to_age(results_event,
                                    control.transition_dating=control.transition_dating)
{
  ggd1 = data.frame(depth=depth[interval],proxy=proxy[interval],
                    x=results_event$linramp$data$x,
                    mean=results_event$linramp$linrampfit$mean,
                    lower=results_event$linramp$linrampfit$q0.025,
                    upper=results_event$linramp$linrampfit$q0.975
                    )
  gg1 = ggplot(data=ggd1,aes(x=depth))+geom_line(aes(y=proxy),col="gray")+
    theme_bw()+ xlim(rev(range(depth[interval])))+xlab("Depth (m)")+
    ylab(expression(paste(delta^18,"O (permil)")))+ggtitle("(a) GI-11 Linear ramp fit")+
    geom_ribbon(aes(x=x,ymin=lower,ymax=upper),fill="red",col="red",alpha=0.3)+
    geom_line(aes(x=x,y=mean),col="blue",size=0.7)

  ybottom = min(results_event$linramp$data$y)
  ytop = min(results_event$linramp$linrampfit$q0.025)
  margt0=results_event$linramp$param$t0$marg.t0
  normt0.y = margt0[,2]/diff(range(margt0[,2]))*(ytop-ybottom)-min(margt0[,2])+ybottom
  gg1 = gg1 + geom_line(data=data.frame(x=margt0[,1],y=normt0.y),aes(x=x,y=y),col="blue")

  margt1 = results_event$linramp$param$t1$marginal
  normt1.y = margt1[,2]/diff(range(margt1[,2]))*(ytop-ybottom)-min(margt1[,2])+ybottom
  gg1 = gg1 + geom_line(data=data.frame(x=margt1[,1],y=normt1.y),aes(x=x,y=y),col="blue",
                        linetype="dashed")

  gg1 = gg1 + geom_vline(aes(xintercept=depth.reference),linetype="dotted",size=0.8)

  gd2 = as.data.frame(results_event$linramp$param$t0$marg.t0)
  gg2 = ggplot(data=gd2,mapping=aes(x=x,y=y)) + geom_line()+theme_bw()+
    xlab("Onset depth (m)") + ylab("Density") + ggtitle("(b) Marginal posterior of onset depth")+
    geom_vline(aes(xintercept = results_event$linramp$param$t0$mean),col="blue")+
    geom_vline(aes(xintercept = results_event$linramp$param$t0$q0.025),col="red")+
    geom_vline(aes(xintercept = results_event$linramp$param$t0$q0.975),col="red")

  gd3 = as.data.frame(results_event$linramp$param$t1$marginal)
  gg3 = ggplot(data=gd3,mapping=aes(x=x,y=y)) + geom_line()+theme_bw()+
    xlab("Onset depth (m)") + ylab("Density") + ggtitle("(c) Marginal posterior of end-point depth")+
    geom_vline(aes(xintercept = results_event$linramp$param$t1$mean),col="blue")+
    geom_vline(aes(xintercept = results_event$linramp$param$t1$q0.025),col="red")+
    geom_vline(aes(xintercept = results_event$linramp$param$t1$q0.975),col="red")

  ggarrange(gg1,ggarrange(gg2,gg3,nrow=1),nrow=2)
  #ggsave("GI-11-rampfit-4800x3000.eps", device=cairo_ps,width=4800,height=3000,units="px",dpi=500,limitsize=FALSE)

  gghist = ggplot(data = data.frame(ages=results_event$event_dating$samples)) + theme_bw()+
    geom_histogram(aes(x=ages,y=..density..),fill="orange",col="black")+xlab("Onset age (yb2k)")+
    ylab("Density") + ggtitle("GI-11 Onset age") +
    geom_vline(aes(xintercept = age.reference),lty=3,size=0.8)+
    geom_vline(aes(xintercept=results_event$event_dating$mean),col="blue",size=0.7)+
    geom_vline(aes(xintercept=results_event$event_dating$q0.025),col="red",size=0.7)+
    geom_vline(aes(xintercept=results_event$event_dating$q0.975),col="red",size=0.7)+
    xlim(rev(range(results_event$event_dating$samples)))

  #ggsave("GI-11-histogram-4800x3000.eps", device=cairo_ps,width=4800,height=3000,units="px",dpi=500,limitsize=FALSE)

@@

```{r events_import, eval=FALSE}
##### IMPORT MYRVOLL-NILSEN 2022 DATA AND COMPARE POSTERIORS ####
library(readxl)
rasmussen_depths = event_intervals$NGRIP_depth_m
rasmussen_ages = event_intervals$GICC_age.yb2k #GISevents$`Age (a b2k)`
buizert_onsets = read_excel("data/Buizert_onsets.xlsx",
                            col_types=c("text","numeric","numeric","numeric","numeric"))
buizert_depths = buizert_onsets$Depth; buizert_ages = buizert_onsets$Age
#buizert_depths[c(2:6,8:9,12:13,15:17,19:21)]
buizert_ages = buizert_ages[c(2:6,8:9,12:13,15:17,19:21)]
capron_onsets_NGRIP_d18O = read_excel("data/Capron_onsets.xls",
                           sheet="d18O",n_max=25)
capron_ages_NGRIP_d18O = capron_onsets_NGRIP_d18O$`t1 (50%)`
capind = numeric(29); buiind = numeric(29)
capind = c(NA,2,3, 4,5,6,NA,NA,7,8,NA,9,10,11,NA,NA,NA,NA,NA,12,13,14,NA,NA,15,NA,NA,16,17)
buiind = c(NA,2,NA,3,4,6,NA,NA,8,9,NA,11,12,13,NA,NA,NA,NA,NA,15,16,17,NA,NA,19,NA,NA,20,21)
```

We then estimate the dating uncertainty for all 29 events
```{r compare_transitions_1}
agesimmatrix_d18O = matrix(NA,29,nsims)
agesimmatrix_d18O_unsync = matrix(NA,29,nsims)
depthlist_d18O = c()
do.plot.rampfit = TRUE
do.plot.agehist = FALSE
depthstats = as.data.frame(matrix(NA,4,29))
colnames(depthstats) = c("true", "mean", "CIL","CIU","dustmean","dustCIL","dustCIU")
agestats = as.data.frame(matrix(NA,4,29))
colnames(agestats) = c("true", "mean", "CIL","CIU","dustmean","dustCIL","dustCIU")
steplengths = rep(0.01,29)
steplengths[21]=0.001 #sometimes changing the steplength slightly might improve convergence (default is 0.01)
for(eventnumber in 1:29){
  transitionlabel = str_sub(event_intervals$onsetlabel[eventnumber],
                      str_locate(event_intervals$onsetlabel[eventnumber],"GI")[1])
  lowerints = which.index(event_intervals$depth_int_lower.m, results_sync$data$depth)
  upperints = which.index(event_intervals$depth_int_upper.m, results_sync$data$depth)
  interval = lowerints[eventnumber]:upperints[eventnumber]

@@

  control.transition_dating=list(label="d18O")
  agetemp_d18O = events_depth_to_age(temp_d18O,control.transition_dating)
  agetemp_d18O_unsync = events_depth_to_age(temp_d18O,
                                            control.transition_dating=list(label="d18O",
                                                                           sync=FALSE))

  agesimmatrix_d18O[eventnumber,] = agetemp_d18O$event_dating$samples 
  agesimmatrix_d18O_unsync[eventnumber,] = agetemp_d18O_unsync$event_dating$samples 
  if(do.plot.agehist){
    hist(agesimmatrix_d18O[eventnumber,],freq=0,breaks=50,col="orange",main=paste0("Onset age: ",transitionlabel),xlab="Age (yb2k)")
    abline(v=age.reference,col="blue")
  }

@@

```{r compare_transitions_2}

  # library(cowplot)

  ggplots = c()

  for(i in 1:29){
    dens = density(agesimmatrix_d18O[i,])
    dens = data.frame(x=dens$x,y=dens$y)#/max(dens2$y))
    densunsync = density(agesimmatrix_d18O_unsync[i,])
    densunsync = data.frame(x=densunsync$x,y=densunsync$y)#/max(dens2$y))
    xlim = rev(range(dens$x,densunsync$x))

    ggd = data.frame(x=dens$x,y=dens$y,x0=densunsync$x,y0=densunsync$y)
    ggdrasmus = data.frame(rasmus=event_intervals$GICC_age.yb2k[i])
    title = str_sub(event_intervals[i,2],str_locate(event_intervals[i,2],"GI-")[1])

    gg = ggplot(data=ggd) + theme_bw()+xlim(xlim)+
      geom_line(aes(x=x0,y=y0),col="gray",size=0.7)+
      geom_line(aes(x=x,y=y),col="black",size=0.7)+
      xlab("Onset year (yb2k)")+ylab("Density") +
      ggtitle(title)+
      theme(axis.text.y=element_blank(),
            axis.ticks.y=element_blank())+
      # geom_vline(aes(xintercept = event_intervals$GICC_age.yb2k[i]),col="blue",size=0.7)
      geom_vline(data=ggdrasmus, aes(xintercept = rasmus),col="blue",size=0.7)

  if(!is.na(buiind[i])){
    ggdbuizert = data.frame(buizert=buizert_onsets$Age[buiind[i]])
    gg = gg + geom_vline(data=ggdbuizert,aes(xintercept = buizert),col="green",size=0.7)
    #abline(v=buizert_onsets$Age[buiind[i]],col="green")
    #abline(v=buizert_ages[buiind[i]],col="green")
  }

  if(!is.na(capind[i])){
    ggdcapron = data.frame(capron=capron_ages_NGRIP_d18O[capind[i]])
    gg = gg + geom_vline(data=ggdcapron,aes(xintercept = capron),col="red",size=0.7)
    # abline(v=capron_ages_NGRIP_d18O[capind[i]],col="red")
  }
    # ggplots = c(ggplots,list(gg))
    ggplots[[i]] = gg
  }

  ggl=ggplot(data.frame(x = 1,x0=1, y = 1,y0=1, rasmus=1,buizert=1,capron=1))+
    geom_line(aes(x=x,y=y,col="Synchronized onset posterior"),size=1)+
    geom_line(aes(x=x0,y=y0,col="Unsynchronized onset posterior"))+
    geom_line(aes(x=x,y=rasmus,col="Rasmussen onset"))+
    geom_line(aes(x=x,y=buizert,col="Buizert onset"))+
    geom_line(aes(x=x,y=capron,col="Capron onset"))+
                        # colour = 'Something2'), aes(x, y, fill = colour))+
  # geom_point(alpha=0, shape = 0)+ # completely transparent rectangular point 
  # scale_fill_manual(values='black', drop=FALSE) +
   # guides(color = guide_legend(override.aes = list(alpha=1, size = 1.3)))+ # showing the point in the legend
    scale_color_manual(values=c("Synchronized onset posterior"="black",
                                "Unsynchronized onset posterior"="gray",
                                "Rasmussen onset"="blue",
                                "Buizert onset"="green",
                                "Capron onset"="red"),
                       labels=c("Synchronized onset posterior",
                                "Unsynchronized onset posterior",
                                "Rasmussen onset",
                                "Buizert onset",
                                "Capron onset"))+
  theme(axis.title = element_blank(),
        axis.text = element_blank(),
        axis.ticks = element_blank(),
        legend.position = c(0.5, 0.5), # move the legend to the center
        legend.title = element_blank(),
        # legend.text = element_text(size = 17),
        legend.key = element_rect(fill='NA'),
        # legend.key.size = unit(0.8,'cm'),
        panel.grid = element_blank(),
        # legend.spacing = unit(3,'cm'),
        # legend.spacing.y = unit(0.5,'cm'),
        panel.border = element_rect(colour = "white", fill='white', size=1)
  )
  ggplots[[30]] = ggl
  ggarrange(plotlist=ggplots,widths=c(6,5))

  # ggsave("allevents-4800x3000.eps",device=cairo_ps,width=4800,height=3000,units="px",limitsize=FALSE)

rownames=c()
for(i in 1:29){
  rownames=c(rownames,str_sub(event_intervals[i,2],str_locate(event_intervals[i,2],"GI-")[1]))
}
#colnames = colnames(depthstats)[1:4]
#colnames = c("name","d18O_mean","d18O_q0.025","d18O_q0.975")
depthresults = t(depthstats)[,2:4]
colnames(depthresults)=c("Z* mean", "Z* q0.025","Z* q0.975")
ageresults = t(agestats[2:4,])
colnames(ageresults)=c("Y* mean", "Y* q0.025","Y* q0.975")
allresults = cbind(depthresults,ageresults)
rownames(allresults)=rownames
latexstr = "Event & Z^* mean (m) & Z^* 95\\% CI (m) & Y^* mean (yb2k) & Y^* 95\\% CI (yb2k) \\\\ \n"
for(i in 1:29){
  latexstr = paste0(latexstr,rownames[i], "& ", format(round(allresults[i,1],2),nsmall=2)," & (", format(round(allresults[i,2],2),nsmall=2), ",
         ",format(round(allresults[i,3],2),nsmall=2),") & ", format(round(allresults[i,4],2),nsmall=2)," & (",format(round(allresults[i,5],2),nsmall=2),", ",format(round(allresults[i,6],2),nsmall=2),") \\\\ \n"
         )
}
cat(latexstr)
```

@@

# Fixed tie-points
ntie = 3
tiesims = matrix(NA,nrow=nsims,ncol=ntie)
tiedepths = c(100,300,600)
tieage = c(450,3000,8500)
